<header style="text-align: center">

### 2019-05-20 report/report.Rmd
Add paged info table and interactive map! (tabbed)

```{r, fig.align='center'}
ddr.map(data$real$routes[1:1000], autocenter = FALSE)
```

@@

@@

@@

The nearby airports to EBBR include:
- EBCI (Brussels South Charleroi)
- EBLF (Liège)
- EHEH (Eindhoven)
- EBAW (Antwerp)
- LFQQ (Lille)

>>>>

@@

## Air Traffic Evolution {.tabset .tabset-fade}

### Static Map {-}

@@

### Interactive Map {-}

```{r, fig.align='center'}
ddr.jsmap(data$real$routes[id %in% div[, id]], info, coord)
```

On average, airlines actually saved `r format(abs(info[, mean(fuel)]), digits = 3)` kg of fuel by diverting flights to airports closer to the origin point.

```{r, fig.align='center'}
datatable(info[, .(orig, dest, airline, diff, fuel)], options = list(dom = 'tp', columnDefs = list(list(className = 'dt-center', targets = '_all'))), colnames = c('Origin', 'Destination', 'Airline', 'Distance Delta (NM)', 'Fuel Delta (kg)')) %>%
	formatRound(columns = c('diff', 'fuel'), digits = 2)
```

@@

The nearby airports to EBBR include:

- EBCI (Brussels South Charleroi)
- EBLF (Liège)
- EHEH (Eindhoven)
- EBAW (Antwerp)
- LFQQ (Lille)

## Traffic in nearby airports

Find # of flights in nearby airports

## Delays in nearby airports
